Data Preparation

### 2019-01-11 Data Preparation.Rmd
change title

# Variable Engineering
##Course Data
The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.

>>>>

# Variable Engineering
##Program Data
The analysis performed on the course data is aimed at discoving what the contribution of each course is towards the fullfilment of the AoDs, and comparing different types of curricula, or programs, based on this infromation.
